\section{Literature Review}

This section presents a comprehensive review of existing research on Backside Power Delivery (BPD) for advanced semiconductor nodes. It covers various design methodologies, optimization techniques, and performance analyses for FinFET and GAA architectures.

\subsection{Current State of BPD Research}

A thorough examination of current literature reveals that BPD networks have been proposed as a solution to the limitations of traditional power delivery methods in advanced nodes. Key studies have highlighted the potential of BPD in enhancing power delivery efficiency and reducing resistive losses.

\begin{table}[htbp]
    \caption{Summary of Key Research Papers on BPD}
    \centering
    \begin{tabular}{l l l}
        \toprule
        \textbf{Author(s)} & \textbf{Title} & \textbf{Key Findings} \\
        \midrule
        Chia et al. \cite{chia2023} & Ultra High Density SoIC & Improved resistance distribution \\
        Chang et al. \cite{chang2024} & EDA Challenges Panel & Addressing system design challenges \\
        Durfee et al. \cite{durfee2023} & GAA Transistor Optimization & Thermal management strategies \\
        Nathan et al. \cite{nathan2023} & 75th Anniversary of the Transistor & Reliability characterization tools \\
        \bottomrule
    \end{tabular}
    \label{tab:key_research}
\end{table}

\subsection{Design Methodologies and Optimization Techniques}

Recent advancements in design methodologies and optimization techniques for BPD networks are explored. This includes discussions on topology optimization, interconnect sizing, and power grid planning to maximize power delivery efficiency and minimize area overhead.

\subsection{Performance and Thermal Analysis}

Performance analysis of BPD networks, including power efficiency, voltage stability, and thermal management, is reviewed. The importance of thermal-aware design techniques and materials with better thermal conductivity in improving the reliability of BPD networks is emphasized.

\subsection{Industry Practices and Standards}

An overview of standard industry practices and guidelines from organizations such as IEEE and leading semiconductor companies is provided. These standards are critical for ensuring the successful implementation and validation of BPD networks in real-world applications.
